\textsf{Are large language models superhuman chemists?}

### 2024-10-29 src/tex/appendix.tex
Update src/tex/appendix.tex
Co-authored-by: Kevin M Jablonka <32935233+kjappelbaum@users.noreply.github.com>
Update appendix.tex

One can observe a clear progression of performance across model families (e.g., \ClaudeThreeFiveSonnet >  \ClaudeThree > \ClaudeTwo or \GPTFourO > \GPTFour > \GPTThreeFiveTurboZeroT). Newer versions consistently outperform their predecessors, indicating improvements in scientific understanding of these model families.
Scores on knowledge-intensive tasks are typically lower than those on calculation and reasoning-intensive questions. Performance on reasoning-intensive questions in \chembench tends to be the highest.

Based on these findings, some scope for improving these models could be to focus on enhancing knowledge-based training, possibly through improved pre-training on chemistry-specific texts or with chemistry knowledge-base integration. However, this type of knowledge should be integrated with sound machine-learning approaches. For example, even \PaperQATwo could not outperform the \gls{llm} using the tools, even though the model now would have access to literature evidence. This suggests we might need an overhaul of how we approach agent building, and how we train models for science applications, since clearly the valuable information stored in textbooks and papers, that can be used to answer questions is not fully leveraged by any of the state-of-the-art models and systems.

>>>>

One can observe a clear progression of performance across model families (e.g., \ClaudeThreeFiveSonnet >  \ClaudeThree > \ClaudeTwo or \GPTFourO > \GPTFour > \GPTThreeFiveTurboZeroT). Newer versions consistently outperform their predecessors.
Scores on knowledge-intensive tasks are typically lower than those on calculation and reasoning-intensive questions. Performance on reasoning-intensive questions in \chembench tends to be the highest.

Based on these findings, some scope for improving these models could be to focus on enhancing knowledge-based training, possibly through improved pre-training on chemistry-specific texts or with chemistry knowledge-base integration. However, this type of knowledge should be integrated with sound machine-learning approaches. For example, even \PaperQATwo could not outperform the \gls{llm} it is using for directing the tools, even though the agent has access to literature evidence. This suggests we might need an overhaul of how we approach agent building, and how we train models for science applications, since clearly the valuable information stored in textbooks and papers, that can be used to answer questions is not fully leveraged by any of the state-of-the-art models and systems.
